leading_cause_of_death_overall

### 2024-03-12 scripts/leading_cause_of_death.Rmd
cleaned up repo + sketches
Cleaned up repository to remove additional/unwanted files. Renamed model. Added sketches. Wrote the README.

```{r}
# create table showing count of deaths by cause (overall)
death_count_by_cause <- nyc_data %>%
  group_by(Leading.Cause) %>%
  summarise(Total_Deaths = sum(as.numeric(Deaths), na.rm = TRUE)) %>%
  arrange(desc(Total_Deaths))
knitr::kable(death_count_by_cause, caption = "Count of Deaths by Leading Cause")
write.csv(death_count_by_cause, "death_count_by_cause.csv", row.names = FALSE)
```

>>>>

```{r}
# create table showing count of deaths by cause (overall)
death_count_by_cause <- nyc_data %>%
  group_by(Leading.Cause) %>%
  summarise(Total_Deaths = sum(as.numeric(Deaths), na.rm = TRUE)) %>%
  arrange(desc(Total_Deaths))
knitr::kable(death_count_by_cause, caption = "Count of Deaths by Leading Cause")
